\documentclass[10pt,letterpaper]{article}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[margin=0.5in]{geometry}
\title{Capstone in Philosophy Writeup/Abstract}
\author{Jeremy Chen}
\date{13/04/2026}
\begin{document}
	\maketitle

Quantum logic is to quantum mechanics as classical logic is to classical mechanics, a way of modeling propositions, their interactions with operations, and consequence. However, quantum logic has one area that it is severely lacking in is the existence of a material conditional. Typically, a material conditional is used to illustrate the consequences ane evolution that one or more propositions could take, but quantum logic lacks that, meaning there's no way to portray the evolution of a quantum system with quantum logic. Given that, this capstone project has focused on looking at non-classical logicks in order to create a suitable framework for quantum logical conditionals. 

The first is modal logic \textbf{B}, considered the smallest of the normal modal logicks. In modal logic \textbf{B}, distributivity is a core part of its material conditional, which violates the core principle of quantum logic, hence its not entirely compatible. The second is linear logic, which makes use of dynamic connectives in order to illustrate the non-reflexive nature of quantum state evolution. However, it falls short in that there are some conflict with the "orthodox" interpretation of quantum mechanics. Finally, is fuzzy logic. Fuzzy logic has been the most promising of the non-classical logicks chosen, given that fuzzy logic admits material conditionals without explicitly enforcing distributivity. Especially the weaker of the fuzzy logics, like MTL, which only gives rules for AND statements, negation, and biconditionals. However, fuzzy logic does not have rules for so called "negative probability", which is a foundational principle within quantum mechanics. 

Given these examined logicks, fuzzy logic is most likely the best analogue for quantum mechanics and is the most worthy of being pursued in the future. 

\end{document}